---
title: "homework-2"
author: Andrew Barefoot
format: pdf
editor: visual
---

## Question 1

install.packages("aRtsy")

Install.packages is how you download a package from a repo and you only have to do it once. When you library something it loads it into the current section. That is something you have to do every R session.

\newpage

# Packages

## Question 2

```{r}
library(aRtsy)
```

The Collatz conjecture is a famous mathematics problem that is unsolved. It states that no matter what positive integer you start with, this sequence will always eventually reach 1.

$f(n) = \begin{cases} n/2 & \text{if } n \equiv 0 \pmod{2} \\ 3n + 1 & \text{if } n \equiv 1 \pmod{2} \end{cases}$

\newpage

## Question 3

#### part a

This function generates artwork based on the sequence. It takes the number in the function and makes that number of random lines.

#### part b

You get a different output every time because it uses R's built in number generator instead of a fixed drawing for each number. 

This is troublesome in the .qmd file because the picture may look different every time you render it. This makes it non-reproducible for anyone else.

Set.seed is an integer vector, containing the random number generator state for random number generation in R. If you use a seed the rondomness will produce the exact same random result every time it is run.

```{r}
set.seed(8)

canvas_collatz(
  colors = c("blue"),
  n = 10
)
```

\newpage